Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

\section{Experimental Arrangement}
A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2 m to 1.2 m above the burner.  One vertical array was centered on the burner and the other vertical array was centered on the right edge of the burner. The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}. Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner. Photographs of the front and rear of the instrumented wall are shown in Figures~{Instrumented_Wall_Front_photo,Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.  The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall. The photograph in Figure~{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
	\caption[Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.]{Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.}
	\label{Instrumented_Wall_Close_up_TC_HF_photo}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
	\caption[Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall]{Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall.}
	\label{Instrumented_Wall_Detail_Rear_TC_photo}
\end{figure}

@@

>>>>

\section{Experimental Arrangement}
A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2 m to 1.2 m above the burner.  One vertical array was centered on the burner and the other vertical array was centered on the right edge of the burner. The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}. Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner. Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.  The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall. The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall. In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Front_photo}\\
	\caption[Photograph of the front side of the instrumented non-combustible wall]{Photograph of the front side of the instrumented non-combustible wall.}
	\label{Instrumented_Wall_Front_photo}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=4.0in]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
	\caption[Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.]{Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.}
	\label{Instrumented_Wall_Close_up_TC_HF_photo}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=4.0in]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
	\caption[Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall]{Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall.}
	\label{Instrumented_Wall_Detail_Rear_TC_photo}
\end{figure}

@@

The results are presented for each of the four burner positions and each of the three fuels.  For the natural gas fueled experiments only two replicates were conducted at each position given the high level of control and repeatability.  For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position.  The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.  The measures of the fire including heat release rate and flame/plume temperatures were also recorded to ensure consistency with the data presented in the previous section.
